## **common chemokine receptor numbering (CRN)**

<br>

#### The existing GPCRdb numbering scheme (see [gpcrdb.org](gpcrdb.org); Pándy-Szekeres, et al. 2023. *Nucleic Acids Research*) was used to refer to structurally equivalent positions across GPCR structures but with numbering that extends toward the receptor N-terminus to encompass a highly conserved Cys residue among chemokine GPCRs, which is designated 1x22. See Methods section of associated paper for details.

<br>

```{r, echo=FALSE, message=FALSE, warning=FALSE}
source("code/000_libraries.R")
data <- read_csv("data/sequence/gpcr/alignment_csv/ALL_classa_df.csv") %>%
  filter(grepl("ccr", protein) | grepl("cxcr", protein) | 
           grepl("ackr", protein) | grepl("xxc", protein) | 
           grepl("cx3c", protein)) %>%
  mutate(protein = toupper(protein)) %>%
  dplyr::select(-seq, -class)
data <- data %>%
  pivot_longer(cols = 2:ncol(data), names_to = "gn", values_to = "resid") %>%
  separate(col = gn, into = c("a", "gn"), sep = "gn", remove = FALSE) %>%
  dplyr::select(-a) %>%
  pivot_wider(names_from = gn, values_from = resid)

```


```{r, echo=FALSE, message=FALSE, warning=FALSE}

reactable(data, filterable = TRUE, defaultPageSize = 23,
          columns = list(
            protein = colDef(style = list(position = "sticky",left = 0,
                                          background ="#fff", zIndex = 1))
  ))

```

