## **common chemokine receptor numbering (CRN)**

<br>

#### The existing GPCRdb numbering scheme (see [gpcrdb.org](gpcrdb.org); Pándy-Szekeres, et al. 2023. *Nucleic Acids Research*) was used to refer to structurally equivalent positions across GPCR structures but with numbering that extends toward the receptor N-terminus to encompass a highly conserved Cys residue among chemokine GPCRs, which is designated 1x22. See Methods section of associated paper for details.

<br>

```{r, echo=FALSE, message=FALSE, warning=FALSE}
source("code/000_libraries.R")
data <- read_csv("data/sequence/gpcr/alignment_csv/ALL_classa_df.csv") %>%
  filter(grepl("ccr", protein) | grepl("cxcr", protein) | 
           grepl("ackr", protein) | grepl("xxc", protein) | 
           grepl("cx3c", protein)) %>%
  mutate(protein = toupper(protein)) %>%
  dplyr::select(-seq, -class)
data <- data %>%
  pivot_longer(cols = 2:ncol(data), names_to = "gn", values_to = "resid") %>%
  separate(col = gn, into = c("a", "gn"), sep = "gn", remove = FALSE) %>%
  dplyr::select(-a) %>%
  pivot_wider(names_from = gn, values_from = resid)

```


```{r, echo=FALSE, message=FALSE, warning=FALSE}

# reactable(data, filterable = TRUE, defaultPageSize = 23,
#           columns = list(
#             protein = colDef(style = list(position = "sticky",left = 0,
#                                           background ="#fff", zIndex = 1))
#   ))

# (1) COLOR ASSIGNMENT
# function that assigns colors to AAs
ResidueZappo <-  function(value){
  color <- case_when(
    value %in% c("R","K","H") ~ "lightblue",
    value %in% c("D","E") ~ "red",
    value %in% c("N","Q","S","T") ~ "lightgreen",
    value %in% c("G","P") ~ "mediumslateblue",
    value %in% c("C") ~ "yellow",
    value %in% c("F","W","Y") ~ "gold",
    value %in% c("A","I","L","M","V") ~ "pink")
}

# function that assigns above function to "background" variable
stylefunc <- function(value) {
  color <- ResidueZappo(value)
  list(background = color)
}

# list giving column formatting (using style function)
coldefs <- list(
  reactable::colDef(style = stylefunc)
)
# get names of cols to format
numcols <- data %>% dplyr::select(2:ncol(data)) %>% colnames()
# replicate list to required length
coldefs <- rep(coldefs,length(numcols))
# name elements of list according to cols
names(coldefs) <- numcols

# (2) "STICKY COL" ASSIGNMENT
# now assign second formatting for "sticky" cols
coldefs2 <- list(
  reactable::colDef(style = list(position = "sticky",left = 0, background ="#fff", zIndex = 1)))

# (3) MERGE FORMATTING
# merge
coldefs <- c(coldefs2, coldefs)

# rename
numcols <- data %>% dplyr::select(1:ncol(data)) %>% colnames()
names(coldefs) <- numcols

# (4) MAKE TABLE
# make table      
reactable(data, filterable = TRUE, defaultPageSize = 23,
          columns = coldefs)

```

