## chemokine & GPCR **cancer-associated variants**

<br>

#### Variant information for all human chemokines and receptors was gathered from The Cancer Genoma Atlas (TCGA), which includes cancer-associated variants from >10,000 individuals and 33 different cancer types [https://www.cancer.gov/tcga](https://www.cancer.gov/tcga). Only missense variants were considered.

<br>

```{r, echo=FALSE, message=FALSE, warning=FALSE}
source("code/000_libraries.R")
a <- read_csv("data/variant/tcga/processed/CK_TCGA_COUNTS.csv")
colnames(a)[2] <- c("CCN or CRN")
b <- read_csv("data/variant/tcga/processed/CKR_TCGA_COUNTS.csv") %>%
    separate(col = gn, into = c("a", "gn"), sep = "gn", remove = FALSE) %>%
  dplyr::select(-a)
colnames(b)[2] <- c("CCN or CRN")
data <- rbind(a,b)
data[is.na(data)] <- 0
rm(a,b)
colnames(data)[3] <- c("no. variants")
```


```{r, echo=FALSE, message=FALSE, warning=FALSE}

reactable(data, filterable = TRUE, defaultPageSize = 20)

```


#### The table includes the following columns:  

- *"protein"* - chemokine or GPCR
- *"CCN or CRN"* - common chemokine or GPCR numbering
- *"no. variants"* - number of cancer-associated variants identified in dataset among queried individuals

